A complete solution for scattering in a kind of quiver gauge theory

### 2025-04-03 Intermediate report/main.tex
New

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{bm}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{enumitem}
\setlist[itemize]{label=\textbullet}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Amplication of BCFW]{A complete solution for scattering in a kind of quiver gauge theory}
\author{Su Yingze}
\institute{Nagoya University}
\date[4 21st 2025]{April 21st 2025}

@@

\end{frame}
\begin{frame}
Note that,
    \begin{enumerate}[label=(\Alph*)]
    \item By property (i), momentum conservation holds for the shifted momenta: $\sum_{i=1}^{n} \hat{p}_i^\mu =0$,
    \item By (ii) and (iii), we have $\hat{p}_i^2=0$, so each shifted momentum is on-shell,
    \item For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$, define $P_I^\mu=\sum_{i\in I}p_i^\mu$.
    \end{enumerate}
Then, $\hat{P}_I^2$ is \textcolor{red}{linear} in z:
\begin{equation*}
    \hat{P}_I^2=\left(\sum_{i\in I} \hat{p}_i \right) ^2 = P_I^2 +2zP_I\cdot R_I \quad \text{with} \quad R_I=\sum_{i\in I} r_i ,
\end{equation*}
because the $z^2$ term vanishes by property (ii). We can write 
\begin{equation*}
    \hat{P}_I^2 = -\frac{P_I^2}{z_I}(z-z_I) \quad \text{with} \quad z_I=-\frac{P_I^2}{2P_I\cdot R_I}
\end{equation*}
\end{frame}
\begin{frame}
    \frametitle{Fantasitic result from Cauchy Theorem}
    As a result of (A) and (B) (momentum conservation and on-shell), we can consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of
    original real momentum. 
    \begin{equation*}
        A_n \longrightarrow \hat{A}_n(z)
    \end{equation*}
    and we have known the possible positions of single poles, $z_I$, different propagators give 
    us different single poles in the z-plane. 
    \par
    \textcolor{red}{$\bigstar$ The most important point is}
    \begin{equation*}
        \boxed{\color{red}A_n=\hat{A}_n(0)}
    \end{equation*}
\end{frame}

>>>>

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{enumitem}
\setlist[itemize]{label=\textbullet}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Amplication of BCFW]{A complete solution for scattering in a kind of quiver gauge theory}
\author{Su Yingze}
\institute{Nagoya University}
\date[4 21st 2025]{April 21st 2025}

@@

\end{frame}
\begin{frame}
Note that,
    \begin{enumerate}[label=(\Alph*)]
    \item By property (i), momentum conservation holds for the shifted momenta: $\sum_{i=1}^{n} \hat{p}_i^\mu =0$,
    \item By (ii) and (iii), we have $\hat{p}_i^2=0$, so each shifted momentum is on-shell,
    \item For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$, define $P_I^\mu=\sum_{i\in I}p_i^\mu$.
    \end{enumerate}
Then, $\hat{P}_I^2$ is \textcolor{red}{linear} in z:
\begin{equation*}
    \hat{P}_I^2=\left(\sum_{i\in I} \hat{p}_i \right) ^2 = P_I^2 +2zP_I\cdot R_I \quad \text{with} \quad R_I=\sum_{i\in I} r_i ,
\end{equation*}
because the $z^2$ term vanishes by property (ii). We can write 
\begin{equation*}
    \hat{P}_I^2 = -\frac{P_I^2}{z_I}(z-z_I) \quad \text{with} \quad z_I=-\frac{P_I^2}{2P_I\cdot R_I}
\end{equation*}
\end{frame}
\begin{frame}
    \frametitle{Fantasitic result from Cauchy Theorem}
    As a result of (A) and (B) (momentum conservation and on-shell), we can consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of
    original real momentum. 
    \begin{equation*}
        A_n \longrightarrow \hat{A}_n(z)
    \end{equation*}
    and we have known the possible positions of single poles, $z_I$, different propagators give 
    us different single poles in the z-plane. 
    \par
    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane, pick a contour that surrounds the simple pole at the origin. 
    \textcolor{red}{$\bigstar$ The most important point here is that}
    \begin{equation*}
        \boxed{\color{red}Res|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
    \end{equation*}
    It means that the orignal ampltude equals to the residue at orign.
\end{frame}
\begin{frame}
    From Cauchy Theorem, we can ontain
    \begin{equation*}
        A_n=-\sum_{z_I}Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.

    Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
    \textcolor{red}{factorizes} into to on-shell parts (Unitarity)
    \begin{equation*}
        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
    This makes it easy to evaluate the residue at $z=z_I$
    \begin{equation*}
        -Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=
    \end{equation*}
\end{frame}
